\mytitle

### 2017-10-27 paper.tex
nits

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{\v{ZooKeeper}\xspace}
\newcommand{\libpaxos}{libPaxos\xspace}
\newcommand{\spaxos}[0]{S-Paxos\xspace}
\newcommand{\crane}[0]{CRANE\xspace}

@@

To find scalability bottlenecks in traditional protocols, we used only one 
client connection and broke down their consensus latency on leader 
(Table~\ref{tab:traditional-latency}). From 3 to 9 replicas, the consensus 
latency (the ``Latency'' column) of these protocols increased more gently than 
that on 24 concurrent connections. For instance, when the number of replicas 
increased from three to nine, ZooKeeper latency increased by 30.3\% with one 
connection; this latency increased by 168.3\% with 24 connections (Figure 1). 
This indicates that concurrent consensus requests are the major scalability 
bottleneck for these protocols.

@@

\textbf{Hard to use.} Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by ZooKeeper.

>>>>

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{ZooKeeper\xspace}
\newcommand{\libpaxos}{libPaxos\xspace}
\newcommand{\spaxos}{S-Paxos\xspace}
\newcommand{\crane}{\textsc{Crane}\xspace}

@@

To find scalability bottlenecks in traditional protocols, we used only one 
client connection and broke down their consensus latency on leader 
(Table~\ref{tab:traditional-latency}). From 3 to 9 replicas, the consensus 
latency (the ``Latency'' column) of these protocols increased more gently than 
that on 24 concurrent connections. For instance, when the number of replicas 
increased from three to nine, \zookeeper latency increased by 30.3\% with one 
connection; this latency increased by 168.3\% with 24 connections (Figure 1). 
This indicates that concurrent consensus requests are the major scalability 
bottleneck for these protocols.

@@

\textbf{Hard to use.} Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by \zookeeper.
